### 2014-06-03 writing/S'14 paper/intro.tex
Revised, more compact intro, and new refs.

Supervised recursive neural network models (RNNs) for sentence meaning
have been successful in a wide array of sophisticated language tasks,
including sentiment analysis \cite{socher2011semi}, analogy completion, image description,
and paraphase detection . These results are encouraging about the
ability of these models to learn compositional semantic grammars, but
it remains an open question whether they can achieve the same results
as grammars based in logical forms when it comes to core semantic
concepts like quantification, entailment, and contradiction defined
over complex linguistic structures. These concepts are central to
robust natural language understanding, so it is essential that our
computational models be able to capture them. % TODO: Insert more citations for past RNN work.

We address this question directly by using a logical grammar togenerate controlled data sets encoding the semantic relationships between pairs of expressions and evaluating whether each of twoclasses of neural model --- plain RNNs and recursive neural tensor networks (RNTNs, \cite{socher2013acl1}) --- can learn those relationships correctly. Following \citet{bowman2013can}, we use the natural logic developed by\cite{maccartney2009extended} as our formal model, which defines seven core relations ofsynonymy, entailment, contradiction, and mutual consistency. Natural logic is well-suited to our purposes because of it defines a rich setof relations between words, phrases, and sentences, and because its logical expressions are derived directly from surface forms, making itamenable to large-scale natural language processing. % Is this the right place for the first self citation?

In our first experiment, we show that both of these models can learn
the core relational algebra of natural logic from data. Our second
experiment builds on this result to cover relations between complex
recursive structures like `(A or B)' and `not(not A and not B)', and
our third experiment involves relations between quantified statements
like `every reptile walks' and `every turtle moves'. We find that the
plain RNN achieves only mixed results on the second and third
experiments, but that the stronger RNTN models generalized well in
every case, suggesting that it has in fact learned, or at least
learned to simulate, our target logical concepts. % TODO: Update with current results

Citations to additional past work to be added.\\...\\...\\...\\...\\...

@@

\subsection{Natural language inference and natural logic}

In its simplest form, \ii{natural language inference} (also known as \ii{recognizing textual entailment}, as in \cite{dagan2006pascal}) is the task of determine whether one sentence entails another. Much of the theoretical work on this task (and some successful implemented models \cite{maccartney2009natural, watanabe2012latent}) involve \ii{natural logic}, formal systems that define sound rules of inference from one sentence of natural language to another without the need for intermediate representations in some other logic. The most powerful model that we are aware of for natural logic is due to MacCartney and Manning \cite{maccartney2009extended} and Icard \cite{icard2012inclusion}, and is centered around the definition of a set of seven logical relations which can hold between sentences, shown in Table \ref{b-table}.

This approach to natural logic can capture much of the complexity of natural language meaning within a well understood framework, and is also fairly straightforward to implement in a machine learning setting since it can be reduced to a seven-way classification problem on sentence pairs. Our goal in this paper is to learn recursive neural network models which are able to mimic key behaviors of this system.

@@

The goal of each of the three experiments that we propose is to learn classifiers that are able to classify pairs of statements from some highly constrained language into these seven classes. It should be noted that this is not a balanced classification problem. If arbitrary pairs of statements are chosen for comparison in almost any domain of natural langauge, the minimally informative \# relation will apply between them. % TODO: How much should we say about this?

@@

Work to date on inference in neural network models is quite limited.
\citet{baroni2012entailment} have achieved limited success in building a classifier to judge entailments between one- and two-word phrases (including some with quantifiers), though their vector representations were crucially based on distributional statistics and were not  learned for the task.
In another line of research, \citet{garrette2013formal} propose a way to improve standard discrete NLI with vector representations. They propose a deterministic inference engine (similar to MacCartney's) which is augmented by a probabilistic component that evaluates individual lexical substitution steps in the derivation using vector representations, though again these representations are not learned, and no evaluations of this system have been published to date.
\label{sec2}

>>>>

Supervised recursive neural network models (RNNs) for sentence meaning
have been successful in a wide array of sophisticated language tasks,
including sentiment analysis \cite{socher2011semi,socher2013acl1},
image description \cite{sochergrounded}, and paraphase detection
\cite{Socher-etal:2011:Paraphrase}. These results are encouraging
about the ability of these models to learn compositional semantic
grammars, but it remains an open question whether they can achieve the
same results as grammars based in logical forms when it comes to core
semantic concepts like quantification, entailment and contradiction.
To date, experimental investigations of these concepts using
distributed representations have been largely confined to short
phrases
\cite{Mitchell:Lapata:2010,Grefenstette-etal:2011,baroni2012entailment,kalchbrenner2014convolutional}.
For robust natural language understanding, we must be able to model
these phenomena in full generality on complex linguistic structures.

We address this question in the context of \ii{natural language
  inference} (also known as \ii{recognizing textual entailment};
\cite{dagan2006pascal}), in which the goal is to determine the core
inferential relationship between two sentences. Much of the
theoretical work on this task (and some successful implemented models
\cite{maccartney2009natural,watanabe2012latent}) involves \ii{natural
  logics}, which are formal systems that define sound rules of
inference between words, phrases, and sentences of language without
the need of intermediate representations in an artificial logical
language. Following \cite{bowman2013can}, we use the natural logic
developed by \cite{maccartney2009extended} as our formal model. This
logic defines seven core relations of synonymy, entailment,
contradiction, and mutual consistency, and it provides rules of
semantic combination for projecting these relations from the lexicon
up to complex phrases. The formal properties and inferential strength
of this system are now well-understood
\cite{Icard:Moss:2013,Icard:Moss:2013:LILT}.

In our experiments, we use this pre-specified logical grammar to
generate controlled data sets encoding the semantic relationships
between pairs of expressions and evaluating whether each of two
classes of neural model --- plain RNNs and recursive neural tensor
networks (RNTNs, \cite{socher2013acl1}) --- can learn those
relationships correctly. In our first experiment, we evaluate the
ability of these models to learn the core relational algebra of
natural logic from data. Our second experiment extends this evaluation
to cover relations between complex recursive structures like `(A or
B)' and `not(not A and not B)', and our third experiment involves
relations between quantified statements like `every reptile walks' and
`every turtle moves'. We find that the plain RNN achieves only mixed
results on all three experiments, whereas the stronger RNTN models
generalized well in every case, suggesting that it has in fact
learned, or at least learned to simulate, our target logical
concepts. % TODO: Update with current results

% Citations to additional past work to be added.\\...\\...\\...\\...\\...

@@

% \subsection{Natural language inference and natural logic}

% In its simplest form, \ii{natural language inference} (also known as \ii{recognizing textual entailment}, as in \cite{dagan2006pascal}) is the task of determine whether one sentence entails another. Much of the theoretical work on this task (and some successful implemented models \cite{maccartney2009natural, watanabe2012latent}) involve \ii{natural logic}, formal systems that define sound rules of inference from one sentence of natural language to another without the need for intermediate representations in some other logic. The most powerful model that we are aware of for natural logic is due to MacCartney and Manning \cite{maccartney2009extended} and Icard \cite{icard2012inclusion}, and is centered around the definition of a set of seven logical relations which can hold between sentences, shown in Table \ref{b-table}.

% This approach to natural logic can capture much of the complexity of natural language meaning within a well understood framework, and is also fairly straightforward to implement in a machine learning setting since it can be reduced to a seven-way classification problem on sentence pairs. Our goal in this paper is to learn recursive neural network models which are able to mimic key behaviors of this system.

@@

% The goal of each of the three experiments that we propose is to learn classifiers that are able to classify pairs of statements from some highly constrained language into these seven classes. It should be noted that this is not a balanced classification problem. If arbitrary pairs of statements are chosen for comparison in almost any domain of natural langauge, the minimally informative \# relation will apply between them. % TODO: How much should we say about this?

@@

% Work to date on inference in neural network models is quite limited.
% \citet{baroni2012entailment} have achieved limited success in building a classifier to judge entailments between one- and two-word phrases (including some with quantifiers), though their vector representations were crucially based on distributional statistics and were not  learned for the task.
% In another line of research, \citet{garrette2013formal} propose a way to improve standard discrete NLI with vector representations. They propose a deterministic inference engine (similar to MacCartney's) which is augmented by a probabilistic component that evaluates individual lexical substitution steps in the derivation using vector representations, though again these representations are not learned, and no evaluations of this system have been published to date.
% \label{sec2}
